---
title: "Age Exchange analyses"
authors: ''
date: ''
output: word_document
---


```{r Import Packages and functions, echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
rm(list=ls())
library(reshape2)
library(FSA)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(RColorBrewer) 
library(knitr)
library(lubridate)
library(dplyr)
library(tidyverse)
library(kableExtra)


# load functions - include the pathway here
load("~ /FunctionsExchange.RData")
```

The `exchangeFuncions.RData` file includes the following functions:

-   **moda**: Function to calculate the most frequent age given by readers.

-   **perc.agr**:100x(no. of readers agreeing with modal age/total no. of readers).

    $$
    PA=100*{X_i \over R }
    $$

    where Xi is the number of readers agreeing with modal age and R is the number of times the fish is aged.

-   **cv**: 100x(standard deviation of age readings/mean of age readings). The equation according to Chang (1982) can be written as:

$$
CV_{j}= 100*\sqrt{\sum_{i=1}^R {(X_{ij} - X_{j})^2 \over X_{j}}}
$$

where CV~j~ is the age precision estimate for the j^th^ fish, x~ij~ is the i^th^ age determination of the j^th^ fish and X~j~ is the mean age estimate of the j^th^ fish

-   **ape**: determinate Average Percentage Error (APE) with modal age. According to Beamish & Fournier (1981) was defined as:

$$
APE_{j}= 100*{1 \over R} \sum_{i=1}^R {|x_{ij} - x_{j}| \over X_{j}}
$$

where x~ij~ is the i^th^ age determination of the j^th^ fish, X~j~ is the mean age estimate of the j^th^ fish, and R is the number of times each fish is aged.

-   **age.nub**: determinate the number of age readings by readers and age group.

-   **age.cv**: calculate the CV by readers and age group.

-   **age.pa**: calculate the PA by readers and age group.

-   **age.bias**: calculate the relative bias by readers and age group.

-   **age.red**: calculate the age composition by readers and age group.

-   **age.sd**: calculate the Standard Deviation (SD) by reader and age group.

-   **age.mean**: calculate the mean age by reader.

-   **testWIL.fun2**: Interbias test and percentage of agreement between readers.\*

-   **abplot**: function to prepare data for the age bias plots.

-   **ageBias.graph**: function to make age bias plots.

APE and the Percentage of Agreement between pairs of readers functions (assigned with \*) are new analysis .


```{r Data description: Import participants table and Age data, echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}

#Participants list
###################

#Need to have the following columns:Participant code and Expertise level
part<-read.csv(file="participants_list.csv",header=T,sep=",")

#Import Age Readings Matrix
df<-read.csv(file="AgeReadingsData.csv",header=T,sep=",")

#Set catch_date as Date (dates should be in the form has day-month-year; month as numeric and year with 4 digits e.g 01-03-2015) 
df$date<-as.Date(df$catch_date,"%d-%m-%Y")

#Set area as factor
df$area<-as.factor(df$area)

#change to a column per each read 
df<-dcast(data = df,formula = SampleID+catch_date+length+area~reader,fun.aggregate = sum, fill=NA_integer_,value.var ="age") 
  ## fill NA_integer_ put NAs in inexisting readings, if we not specify fill it will put 0 (zeros)
```

The next field needed to be manually changed for each different analysis. It should include the columns number corresponding to:

-   the readers, information of the fish (i.e. sample ID, sex, length, date of catch),

-   the readers and modal age, the length, readers and modal age and

-   the maximum age of the sample data.

In this case  column numbers are:

```{r Fields that change! To be checked and replaced, echo=TRUE, message=FALSE, warning=FALSE,linewidth=60}

#Name of readers
readers<-as.vector(colnames(df[,5:24]))

#columns with info
col.info<-1:4

#columns with readers
col.read<-5:24

#columns with readers and modal age
col.mod<-5:25

#columns with length, readers and modal age
col.len<-c(3,5:25)

# maximo age
age.max<-max(df[,5:24],na.rm=T)
```

The following chunk make a lists of readings per areas. In this example there are 2 areas, so it will create a list with area A, area B and a list with area A plus area B. Also the PA, CV and APE are calculated.

```{r Make a list for each area to calculate PA,linewidth=60}
## make list
a<-list() 
# 
# Make a table per area
for (i in levels(as.factor(df$area))){
  a[[i]]<-subset(df,area==i)
}

##Add a list with all areas
a[["all"]] <- df

# Add Modal Age
a.allr<-mapply(cbind, a, "modal.age"=lapply(lapply(a,"[",col.read),moda), SIMPLIFY=F)

#Determine Percentage of Agreement
a.allr<-mapply(cbind, a.allr, "pa"=lapply(lapply(a.allr,"[",c(col.read, max(col.read+1))),perc.agr), SIMPLIFY=F)

#Calculate CV
a.allr<-mapply(cbind, a.allr, "cv"=lapply(lapply(a.allr,"[",c(col.read, max(col.read+1))),cv), SIMPLIFY=F)

#Add APE
a.allr<-mapply(cbind, a.allr, "ape"=lapply(lapply(a.allr,"[",col.read),ape), SIMPLIFY=F)


#Quando a idade modal ? 0 e a perc de concordancia ? 100% o CV n?o pode ser calculado. No entanto este valor ? 0. Substituir manualmente.

func<-function(x){
  x[,"cv"][x[,"pa"]==100]<-0
  x[,"ape"][x[,"pa"]==100]<-0
  return(x)
}

a.allr<-lapply(a.allr,func)
```

The following chunks doesn't need to be changed and the report output starts from here.



### Participant table {.unnumbered}

The participant table indicate the readers involved in the analysis, its level of expertise and the code that will be used along the following analysis.

```{r Participants table, echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
kable(part,"pandoc",caption="Participants list")
```

#### Sample Overview {.unnumbered}

The sample overview table resume the number of otoliths per semester, area, and its length range.

```{r Samples Overview, echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE,linewidth=60}
# Overview of samples
samp<-df[,col.info] 
samp$semester<-semester(as.Date(df$catch_date,"%d-%m-%Y"))

sa<-aggregate( length~area+semester,samp,range)
pl<-data.frame(table(samp$area,samp$semester))

colnames(pl)<-c("area","semester","n.samples")
overv<-merge(sa,pl,by=c("area","semester"))


kable(cbind(overv[,c(1:2,4)],"Min Length"=(overv$length[,1]),"Max Length"=(overv$length[,2])),"pandoc",caption = "Sample Overview")
```

### Exploratory Analysis {.unnumbered}

The following lines of code make the first look on the data, to see the length distribution of the samples and the mean at age by reader.

```{r Exploratory Analysis, echo=TRUE, message=FALSE,linewidth=60, warning=FALSE}
#Distribution length
options(digits=4)
df1<-df
df1$tl_class<-floor(df1$length*.1) # length class

#Length distribution - Basic plot
a1<-ggplot(df1, aes(fill=area, x=tl_class)) + 
    geom_bar(position = "stack") #

# Length distribution
fig1<-a1+theme(plot.title=element_text(size=18,face="bold"),    
               axis.text.y = element_text(size=12), 
               axis.text.x = element_text(size=12),
               axis.title.x = element_text(size=16),
               axis.title.y = element_text(size=16))+
  theme(legend.title = element_blank(),legend.position="top")+
  scale_x_continuous("Total length, cm")+
   scale_y_continuous("Number")

#Mean length at age
df.m1<-lapply(lapply(a,"[",c(col.read[1]-2,col.read)),me.len)


df.m2<-melt(df.m1)
  colourCount = length(unique(df.m2$Var1))
    getPalette = colorRampPalette(brewer.pal(9, "Set1"))
order.area<-c("A","B","all") # order areas by appearance you want 
df.m2$L1<-ordered(df.m2$L1,levels=order.area)

# Mean Length at Age plot    
fig2<-  ggline(df.m2,x="Var2",y="value",color = "Var1",size = 1,palette =getPalette(colourCount),ylab="Total length,mm", xlab="Mean Age")+theme(legend.title=element_blank(),legend.position="top",legend.box = "horizontal")+guides(fill=guide_legend(nrow=2,byrow = T))+facet_wrap(~L1)
```

#### Total length distribution by areas {.unnumbered}

Figure 1 presents the length distribution by area. The advantage is to have a first look of the data.

```{r Lenght Distribution Sample, echo=TRUE, message=FALSE,linewidth=60, warning=FALSE}
fig1
```

#### Mean Length at Age {.unnumbered}

Figure 2 is the mean length at age of each individual reader. This type of analysis allow to check if all readers have the same age trend.

```{r Mean Lenght at Age, echo=TRUE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
fig2
```

### Age Comparations Analysis: All readers {.unnumbered}

The next lines calculate the PA, CV and APE by areas, age and readers, following the same approach described in Eltink spreadsheet.

```{r Tabelas Eltink, echo=TRUE, message=FALSE, warning=FALSE, linewidth=60}
#table with cv and PA by areas
pa_cv.areas<-sapply(lapply(a.allr,"[",c(max(col.read)+2):ncol(a.allr[[1]])), function (x) lapply(lapply(x, mean, na.rm=TRUE),round,1))

# Number of otolith readied by reader and age group
#############################################
age.reding<-lapply(lapply(a.allr,"[",col.mod),age.red)

# Coefficient of variation by reader and age
#############################################
cv.age.reader<-lapply(lapply(a.allr,"[", c(readers,"modal.age","cv")),age.cv)

# Percentage of agreement by reader and age
############################################
agree<-lapply(lapply(a.allr,"[",col.mod),age.pa)

# Relative Bias by reader and modal age
#######################################
rel.bias<-lapply(lapply(a.allr,"[",col.mod),age.bias)

# Age Composition
###################
age.comp<-lapply(lapply(a.allr,"[",col.mod),age.red)

# 2x Standard Deviation
########################
stand<-lapply(lapply(a.allr,"[",col.mod),age.sd)

# Age Mean
############
me<-lapply(lapply(a.allr,"[",col.mod),age.mean)

#Mean Length at age
######################
me.age.len<-lapply(lapply(a.allr,"[",col.len),me.len)

# Interbias and and percentage of agreement between readers
###########################################################
bias<-lapply(lapply(a.allr,"[", col.mod),testWIL.fun2)

#Age Bias Plots
################
li.all<-mapply(abplot,me,stand,SIMPLIFY = F)
```

#### Table with PA, CV, APE by samples {.unnumbered}

```{r Table 1, echo=TRUE, results="asis"}
options(knitr.kable.NA ="")
  kable(x = a.allr$all, "pandoc",caption = "Table with samples")
```

#### Percentage of agreement, Coefficient of variation and Average percentage error {.unnumbered}

```{r tab3.1.1, echo=TRUE}
kable(t(pa_cv.areas),"pandoc",caption = "Percentage of agrement (PA),coeficient of variation (CV) and Average Percent Error (APE) for all readers analysis")
```

#### Number of samples by reader and age group {.unnumbered}

```{r echo=TRUE, results="asis"}
options(knitr.kable.NA ="")
for(i in names(age.reding)) {
  print(kable(x = age.reding[i], "pandoc",caption = paste("Age Readings table for the", i, "area by age",sep=" ")))
  cat("\n")
}

```

#### CV by reader and age {.unnumbered}

```{r cv table,results="asis", echo=TRUE}
options(knitr.kable.NA ="")
for(i in names(cv.age.reader)) {
  print(kable(cv.age.reader[i],"pandoc", caption = paste("Coeficiente of variation (CV) for",i,"area",sep=" ")))
}
```

#### PA by reader and age {.unnumbered}

```{r pa table,results="asis", echo=TRUE}
options(knitr.kable.NA ="")
for(i in names(agree)) {
  print(kable(agree[i],"pandoc", caption = paste("Percentage of Agreement (PA) for",i,"area",sep=" ")))
}
```

#### Relative bias by reader and age {.unnumbered}

```{r,results="asis", echo=TRUE}
options(knitr.kable.NA ="")
for(i in names(rel.bias)) {
  print(kable(rel.bias[i],"pandoc", caption = paste("Relative bias for",i,"area",sep=" ")))
}
```

#### Age composition {.unnumbered}

```{r Age Composition, echo=TRUE,results="asis", message=FALSE, warning=FALSE}
for(i in names(age.comp)) {
  print(kable(age.comp[i],"pandoc", caption = paste("Age Composition for",i,"area",sep=" ")))
}
```

#### Standard deviation {.unnumbered}

```{r table standart deviation,results="asis", echo=TRUE}
for (i in names(stand)){
print(kable(stand[i],"pandoc",caption = paste("2x Standart Deviation for",i,"area",sep=" ")))
}
```

```{r Table mean age,results="asis",echo=TRUE}
for (i in names(me)){
print(kable(me[i],"pandoc",caption = paste("Mean Age by reader for",i,"area",sep=" ")))
}
```

#### Mean Length at Age {.unnumbered}

```{r table mean length at age,echo=TRUE, resusts="asis"}
for (i in names(me.age.len)){
print(kable(me.age.len[i],"pandoc",caption = paste("Mean Length at age for",i,"area",sep=" ")))
}
```

```{r tab3.1.2, echo=TRUE}
options(knitr.kable.NA ="-")
options(digits = 1)


 az<-rbind(do.call(rbind,
 lapply(agree,"[",i="all",j=1:(age.max+1))),do.call(rbind,
 lapply(cv.age.reader,"[",i="ALL",j=1:(age.max+1))),do.call(rbind,
 lapply(rel.bias,"[",i="all",j=1:(age.max+1))))
```

```{r tab 3.2.3, echo=FALSE}
options(knitr.kable.NA ="-")
options(digits = 1)
kable(az,"pandoc",caption="Percentage of agrement (PA),coeficient of variation (CV) and bias for all areas by age group")
```

#### PA, CV and SD vs Modal Age {.unnumbered}

The coefficient of variation (CV%), percent agreement and the standard deviation (SD) are plotted against MODAL age. CV is much less age dependent than the standard deviation (SD) and the percent agreement. CV is therefore a better index for the precision in age reading. Problems in age reading are indicated by relatively high CV's at age (Eltink et al., 2002).

```{r Fig- CV PA SD, echo=TRUE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
options(digits=1)
b<-rbind(do.call(cbind,lapply(cv.age.reader,"[",i="ALL",j=1:(age.max+1))),do.call(cbind,lapply(agree,"[",i="all",j=1:(age.max+1))),do.call(cbind,lapply(stand,"[",i="All Readers",j=1:(age.max+1))))

met<-rep(c("CV","PA","SD"),each=(age.max+1),times=1)
b<-sapply(as.data.frame(b,row.names = F),as.numeric)
b<-melt(b)
b$age<-rep(0:age.max,times=3)
b$var<-met
colnames(b)[2]<-"variable"

fig3<-ggplot(b,aes(x=age,color= var))+geom_line(data=subset(b,var=="PA"),aes(y=value,color=var),size=1.2)+
   geom_line(data=subset(b,var=="CV"),aes(y=value,color=var),size=1.2)+
   geom_line(data=subset(b,var=="SD"),aes(y=value*10,color=var),size=1.2)+geom_point(data=subset(b,var=="PA"),aes(y=value,color=var),size=2)+
   geom_point(data=subset(b,var=="CV"),aes(y=value,color=var),size=2)+
   geom_point(data=subset(b,var=="SD"),aes(y=value*10,color=var),size=2)+
  theme_bw()+facet_wrap(~variable)+ylab("Percentage, %")+scale_y_continuous(sec.axis = sec_axis(~./10, name = "Standart deviation, %"))+theme(legend.title = element_blank())

 fig3
```

#### Age Bias Plots {.unnumbered}

To make the age bias plots, it's need to include in the `ageBias.graph`function the exercise name and witch type of analysis it is performed i.e, "all readers", "expert readers" or "trainee readers".

```{r fig 3.1.3-Age Bias Plots, echo=TRUE, fig.height=8, fig.width=6, message=FALSE, warning=FALSE}
ageBias.graph(li.all,"Simulated Exchange","all readers")
```

#### Inter readers test and agreement {.unnumbered}

```{r Inter reader test and agreement, echo=TRUE, message=FALSE, warning=FALSE, results="asis"}
for (i in names(bias)){
print(kable(bias[i],"pandoc",caption = paste("InterBias and percentage of agreement between readers for",i,"area",sep=" "))%>%
      kable_styling(latex_options="scale_down"))
  
  cat("\n")
}
```

For the analysis using only expert or trainee readers, we will select from the main age matrix the readers by expertise and re-run the code lines described above.

#### Extra Plots {.unnumbered}

```{r Extra Plot, echo=TRUE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}

# Mean Length at Age - Plot (EXTRA)

#Total length column
df1<-lapply(a,"[",c("length",readers))
mean.df1<-lapply(df1,me.len)

mean.df1<-melt(mean.df1)
 colourCount = length(unique(mean.df1$L1))
 getPalette = colorRampPalette(brewer.pal(9, "Set1"))


        mean.df1$Var1<-ordered(mean.df1$Var1,levels=readers)
 
ggline(mean.df1,x="Var2",y="value",color = "L1",size = 1,ylab="Total length,mm", palette =getPalette(colourCount), xlab="Mean Age")+ theme(legend.title=element_blank())+facet_wrap(~Var1)
```

```{r box-plots,fig.height=4,fig.width=10, echo=TRUE}
wkcav<-melt(a.allr$all[1:24], id=(c("SampleID","catch_date", "length","area")))

#column names
colnames(wkcav)[5]<-"readers"
colnames(wkcav)[6]<-"age"


#Order
wkcav$age <- ordered(wkcav$age,levels = c("0", "1", "2","3",
                                         "4","5","6","7","NA"))

fig4<-ggplot(subset(wkcav,!wkcav$age=="NA"), aes(age,length,fill=area)) + geom_boxplot() +
  xlab("Age, years")+ ylab("Length, cm") +
  facet_wrap(~readers,nrow = 2)+theme_bw() +
  theme(strip.text.y = element_text()) +
  theme(axis.text.x = element_text(size=10),
        plot.title=element_text(size=10,face="bold"),
        axis.text.y = element_text(size=10),
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        strip.text.x = element_text(size = 10))
fig4

```

### Age Comparations Analysis: Expert readers {.unnumbered}

The following lines of code are referent to the analysis using only expert readers.

```{r Expert readers analysis, message=FALSE, warning=FALSE}
adv<-droplevels(subset(part,ExpertiseLevel=="Advanced"))
adv<-levels(as.factor(adv$ParticipantCode))

# Select readers by expertise level
df.adv <-lapply(a,"[",c(colnames(a$all)[col.info],adv))

#Add Modal Age
df.adv <-  mapply(cbind, df.adv, "modal.age"=lapply(lapply(df.adv,"[",adv),moda), SIMPLIFY=F)

#Add PA
df.adv<-  mapply(cbind, df.adv, "pa"=lapply(lapply(df.adv,"[",c(adv,"modal.age")),perc.agr), SIMPLIFY=F)

#Add cv
df.adv<-mapply(cbind, df.adv, "cv"=lapply(lapply(df.adv,"[",c(adv,"modal.age")),cv), SIMPLIFY=F)

##Add APE
df.adv<-mapply(cbind, df.adv, "ape"=lapply(lapply(df.adv,"[",adv),ape), SIMPLIFY=F)


 df.adv<-lapply(df.adv,func)
 
 ##OUTPUT 
#Mean PA, CV and APE

pa_cv.adv<-sapply(lapply(df.adv,"[",c("pa","cv","ape")), function (x) lapply(lapply(x, mean, na.rm=TRUE),round,1))

#Other tables 

age.reding.adv<-lapply(lapply(df.adv,"[",c(adv,"modal.age")),age.red)
agree.adv<-lapply(lapply(df.adv,"[",c(adv,"modal.age")),age.pa)
cv.adv<-lapply(lapply(df.adv,"[",c(adv,"modal.age","cv")),age.cv)
bias.adv<-lapply(lapply(df.adv,"[",c(adv,"modal.age")),age.bias)
stand.adv<-lapply(lapply(df.adv,"[",c(adv,"modal.age")),age.sd)
me.adv<-lapply(lapply(df.adv,"[",c(adv,"modal.age")),age.mean)
IntBias.adv<-lapply(lapply(df.adv,"[", c(adv,"modal.age")),testWIL.fun2)
me.age.len.adv<-lapply(lapply(df.adv,"[",c("length",adv,"modal.age")),me.len)
```

#### PA, CV and APE {.unnumbered}

```{r PA CV APE adv, echo=FALSE}
kable(t(pa_cv.adv),"pandoc",caption = "Percentage of agrement (PA),coeficient of variation (CV) and Average Percent Error (APE) for expert readers analysis")
```

#### Number of age readings {.unnumbered}

```{r Number of age readings adv, echo=FALSE}
for(i in names(age.reding.adv)) {
  print(kable(x = age.reding.adv[i], "pandoc",caption = paste("Age Readings table for the", i, "area by age",sep=" ")))
  cat("\n")
}
```

#### Coefficient of variation by age and reader {.unnumbered}

```{r CV readers, echo=FALSE}
for(i in names(cv.adv)) {
  print(kable(cv.adv[i], "pandoc",caption = paste("Coefficient of Variation (CV) by reader for",i,"area by age",sep=" ")))
  cat("\n")
}
```

#### PA by age and reader {.unnumbered}

```{r PA adv readers, echo=FALSE}
for(i in names(agree)) {
  print(kable(agree[i], "pandoc",caption = paste("Percentage of Agreement (PA) by reader for",i,"area by age",sep=" ")))
  cat("\n")
}
```

#### Relative Bias by age and reader {.unnumbered}

```{r bias adv readers, echo=FALSE}
for(i in names(cv.adv)) {
  print(kable(cv.adv[i], "pandoc",caption = paste("Coefficient of Variation (CV) by reader for",i,"area by age",sep=" ")))
  cat("\n")
}
```

#### 2x Standard Deviation {.unnumbered}

```{r table standart deviation for adv readers,results="asis", echo=FALSE}
for (i in names(stand.adv)){
print(kable(stand.adv[i],"pandoc",caption = paste("2x Standart Deviation for",i,"area",sep=" ")))
  cat("\n")
}
```

#### Mean Age {.unnumbered}

```{r Table mean age for adv readers, echo=FALSE}
for (i in names(me.adv)){
print(kable(me.adv[i],"pandoc",caption = paste("Mean Age by reader for",i,"area",sep=" ")))
  cat("\n")
}
```

#### Mean Length at Age {.unnumbered}

```{r table mean length at age for adv readers, echo=FALSE}
for (i in names(me.age.len.adv)){
print(kable(me.age.len.adv[i],"pandoc",caption = paste("Mean Length at age for",i,"area",sep=" ")))
  cat("\n")
}
```

#### PA, CV and Bias by age group {.unnumbered}

```{r arranje data 3.3, include=FALSE}
options(digits = 1)
az.adv<-rbind(do.call(rbind,
 lapply(agree.adv,"[",i="all",j=1:(age.max+1))),do.call(rbind,
 lapply(cv.adv,"[",i="ALL",j=1:(age.max+1))),do.call(rbind,
 lapply(bias.adv,"[",i="all",j=1:(age.max+1))))

#Necess?rio acrescentar linhas a indicar % agree, %CV e bias na tab
```

```{r tab, echo=FALSE}
options(knitr.kable.NA ="-")
options(digits = 1)
kable(az.adv,"pandoc",caption="Percentage of agrement (PA),coeficient of variation (CV) and bias for all areas by age group")
```

#### Coefficient of variation, % agreement and Standard deviation by modal age {.unnumbered}

```{r echo=FALSE, fig.height=4, fig.width=6}
b.adv<-rbind(do.call(cbind,lapply(cv.adv,"[",i="ALL",j=1:(age.max+1))),do.call(cbind,lapply(agree.adv,"[",i="all",j=1:(age.max+1))),do.call(cbind,lapply(stand.adv,"[","All Readers",j=1:(age.max+1))))

met<-rep(c("CV","PA","SD"),each=8,times=1)
b.adv<-sapply(as.data.frame(b.adv,row.names = T),as.numeric)
b.adv<-melt(b.adv)
b.adv$age<-rep(0:7,times=3)
b.adv$var<-met
colnames(b.adv)[2]<-"variable"


ggplot(b.adv,aes(x=age,y=value,color= var))+geom_line(data=subset(b.adv,var=="PA"),aes(color=var),size=1.2)+
  geom_line(data=subset(b.adv,var=="CV"),aes(color=var),size=1.2)+
  geom_line(data=subset(b.adv,var=="SD"),aes(y=10*value,color=var),size=1.2)+geom_point(data=subset(b.adv,var=="PA"),aes(y=value,color=var),size=2)+
   geom_point(data=subset(b.adv,var=="CV"),aes(y=value,color=var),size=2)+
   geom_point(data=subset(b.adv,var=="SD"),aes(y=value*10,color=var),size=2)+ ylab("Percentage, %")+scale_y_continuous(sec.axis = sec_axis(~./50, name = "Standard deviation"))+theme_bw()+facet_wrap(~variable)
```

#### Age Bias Plots {.unnumbered}

```{r age bias plots; adv readers, fig.height=6, fig.width=10, echo=FALSE}
li.adv<-mapply(abplot,me.adv,stand.adv,SIMPLIFY = F)
ageBias.graph(li.adv,"simulated Exchange","Advanced Readers")
```

#### Inter readers test and agreement between each reader {.unnumbered}

```{r InterBias adv readers, echo=FALSE}
for (i in names(IntBias.adv)){
print(kable(IntBias.adv[i],caption = paste("InterBias and percentage of agreement between readers for",i,"area",sep=" ")))
  cat("\n")
}
```

```{r Mean length at Age - Extra Plot, echo=TRUE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}

# Mean Length at Age - Plot (EXTRA)

#preciso coluna com comprimento 
df.adv1 <-lapply(a,"[",c("length",adv))
mean.adv<-lapply(df.adv1,me.len)

mean.adv<-melt(mean.adv)
 colourCount = length(unique(mean.adv$L1))
 getPalette = colorRampPalette(brewer.pal(9, "Set1"))


  #zz.main<-c("Reader.1" ,"Reader.2","Reader.4","Reader.5","Reader.14","Reader.15") 
      mean.adv$Var1<-ordered(mean.adv$Var1,levels=adv)
 
ggline(mean.adv,x="Var2",y="value",color = "L1",size = 1,ylab="Total length,mm", palette =getPalette(colourCount), xlab="Mean Age")+ theme(legend.title=element_blank())+facet_wrap(~Var1)
```

### Age Comparations Analysis: Trainee readers {.unnumbered}

The following lines of code are referent to the analysis using only trainee readers.

```{r Trainee readers analysis, message=FALSE, warning=FALSE}
bas<-droplevels(subset(part,ExpertiseLevel=="Trainee"))
bas<-levels(as.factor(bas$ParticipantCode))

# Select readers by expertise level
df.bas <-lapply(a,"[",c(colnames(a$all)[col.info],bas))



#Add Modal Age
df.bas<-   mapply(cbind, df.bas, "modal.age"=lapply(lapply(df.bas,"[",bas),moda), SIMPLIFY=F)

#Add PA
df.bas<-  mapply(cbind, df.bas, "pa"=lapply(lapply(df.bas,"[",c(bas,"modal.age")),perc.agr), SIMPLIFY=F)

#Add cv
df.bas<-mapply(cbind, df.bas, "cv"=lapply(lapply(df.bas,"[",c(bas,"modal.age")),cv), SIMPLIFY=F)


##Add APE
df.bas<-mapply(cbind, df.bas, "ape"=lapply(lapply(df.bas,"[",bas),ape), SIMPLIFY=F)


# #Quando a idade modal ? 0 e a perc de concordancia ? 100% o CV n?o pode ser calculado. No entanto este valor ? 0. Substituir manualmente.
 
func<-function(x){
  x[,"cv"][x[,"pa"]==100]<-0
  x[,"ape"][x[,"pa"]==100]<-0
  return(x)
}


 df.bas<-lapply(df.bas,func)
 
 ##OUTPUT 
#Mean PA, CV and APE

pa_cv.bas<-sapply(lapply(df.bas,"[",c("pa","cv","ape")), function (x) lapply(lapply(x, mean, na.rm=TRUE),round,1))

#Other tables 
age.reding.bas<-lapply(lapply(df.bas,"[",c(bas,"modal.age")),age.red)
agree.bas<-lapply(lapply(df.bas,"[",c(bas,"modal.age")),age.pa)
cv.bas<-lapply(lapply(df.bas,"[",c(bas,"modal.age","cv")),age.cv)
bias.bas<-lapply(lapply(df.bas,"[",c(bas,"modal.age")),age.bias)
stand.bas<-lapply(lapply(df.bas,"[",c(bas,"modal.age")),age.sd)
me.bas<-lapply(lapply(df.bas,"[",c(bas,"modal.age")),age.mean)
IntBias.bas<-lapply(lapply(df.bas,"[", c(bas,"modal.age")),testWIL.fun2)
me.age.len.bas<-lapply(lapply(df.bas,"[",c("length",bas,"modal.age")),me.len)
```
```{r}
sessionInfo()
```

